\section{The Fundamental Matrix}\label{sec:fm}
In this section, we begin by defining the fundamental matrix. Next, we outline numerical methods for estimating the fundamental matrix using point correspondences between two images. We start by using linear equations from epipolar constraints to build a basic framework. Then, we delve into \ac{GH} \cite{12-gauss-helmert} to improve precision and robustness in our analysis. A similar approach will be carried out for the \acs{TFT} later on (Section \ref{sec:tft}).

\subsection{Definition}
The \ac{FM} is defined by the equation
\begin{equation}
	x'^\top Fx = 0
	\label{eq:fmDef}
\end{equation}

for any pair of matching points \( x \leftrightarrow x' \) in two images. 

\subsection{Linear Computation}
Given sufficiently many point matches (\ie, at least 7), Equation (\ref{eq:fmDef}) can be used to compute the unknown matrix \( F \). In particular, each point match gives rise to one linear equation in the unknown entries of \( F \). Specifically, the equation corresponding to a pair of points \( (x, y, 1) \) and \( (x', y', 1) \) is
\begin{equation}
	x'xf_{11} + x'yf_{12} + x'f_{13} + y'xf_{21} + y'yf_{22} + y'f_{23} + xf_{31} + yf_{32} + f_{33} = 0.
\end{equation}

From a set of \( n \) point matches, we derive the set of linear equations

\begin{equation}
	Af = 
	\begin{bmatrix}
	x_1'x_1 & x_1'y_1 & x_1' & y_1'x_1 & y_1'y_1 & y_1' & x_1 & y_1 & 1\\
	\vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \vdots\\
	x_n'x_n & x_n'y_n & x_n' & y_n'x_n & y_n'y_n & y_n' & x_n & y_n & 1
	\end{bmatrix}
	f = 0,
	\label{eq:LinearFM}
\end{equation}

where \( f \) is the 9-vector made up of the entries of \( F \) in row-major order.\\

The 8-point algorithm stands as the most straightforward approach for computing the \acs{FM}. This involves constructing and solving a set of linear equations, typically using the least squares method. The original algorithm is due to \cite{11-eight-point-algo}.

\begin{algorithm}[h]
		\caption{Normalized Eight Point Algorithm (\acs{L-FM})}
		\kwObjective{Given \( n \geq 8 \) image point correspondences \( \{ x_i \leftrightarrow x'_i \} \), determine the fundamental matrix \( F \) such that \( {x'}_i^\top Fx_i = 0 \).}
		\kwAlgorithm{
		\begin{enumerate}[label=(\roman*),leftmargin=*,rightmargin=1.5em]
        	\item \textbf{Normalization:} Transform the image coordinates according to \( \hat{x}_i = Tx_i \) and \( \hat{x}'_i = Tx_i' \), where \( T \) and \( T' \) are normalizing transformations consisting of a translation and a scaling.
        	\item Find the Fundamental Matrix \( \hat{F}' \) corresponding to the matches \( \{ x_i \leftrightarrow x'_i \} \) by
       		\begin{enumerate}[label=(\alph*),leftmargin=*,rightmargin=1.5em]
       			\item \textbf{Linear solution:} Determine \( \hat{F} \) from the singular vector corresponding to the smallest singular value of \( \hat{A} \), where \( \hat{A} \) is composed from the matches \( \{ x_i \leftrightarrow x'_i \} \) as defined in Equation (\ref{eq:LinearFM}).
       			\item \textbf{Constraint enforcement:} Replace \( \hat{F} \) by \( \hat{F}' \) such that \( |\hat{F}'| = 0 \) using the SVD.
       		\end{enumerate}
        	\item \textbf{Denormalization:} Set \( F = T'^\top \hat{F}'T \). Matrix \( F \) is the fundamental matrix corresponding to the original data \( \{ x_i \leftrightarrow x'_i \} \).
    	\end{enumerate}
    }
    \label{algo:LFM}
\end{algorithm}

\pagebreak

\subsection{Optimized Computation}

\begin{algorithm}[h]
		\caption{\acs{GH} Algorithm for the \acs{FM} (\acs{O-FM})}
		\kwObjective{Given \( n \geq 8 \) image point correspondences \( \{ x_i \leftrightarrow x'_i \} \), determine the fundamental matrix \( F \) such that \( {x'}_i^\top Fx_i = 0 \).}
		\kwAlgorithm{
		\begin{enumerate}[label=(\roman*),leftmargin=*,rightmargin=1.5em]
        	\item \textbf{Initial Linear Estimation:} Algorithm (\ref{algo:LFM}).
        	\item \textbf{Optimization:} Apply \acs{GH} to iteratively reduce the estimation error.
    	\end{enumerate}
    }
\end{algorithm}
